---
title: "Homework 1-Question 2"
output: html_document
---

## Homework 1-Question 2

We worked on the Boston house price dataset that is already available in library MASS. Aim is to understand if certain variables explain the variability better than the others. We looked at the general structure and summary of the data and also correlation matrix to get a sense of correlations between variables. 

```{r}
library(MASS)
data <- Boston
summary(data)
cor(data)
```

We performed PCA and commented on how much of the variability is explained by which components. While performing the PCA, we perform the calculations on correlation matrix with cor=TRUE, ensuring scaling amongst the variables. PCA returns 14 components corresponding to the dataset. We see that 46% of the variability can be explained by Component 1 alone, and Proportion of Variance goes down from there. We have chosen our treshold as 90% for this dataset, so we will make use of first 8 components explanining 92% of the variability. Original attributes' mapping to these components can be observed from Loadings.

```{r}
pca <- princomp(data,cor = TRUE)
summary(pca,loadings = TRUE)
```

Variances explained by the components can also be seen in the plot. 

```{r}
plot(pca)
```

